Supplementary material

### 2018-06-06 Manuscript/ms.tex
Cleaning up caveats

In addition, it is important to note that that the data to which we fit our model implicitly reflect the control efforts already enacted by the city.
These control efforts are guided by the MI-Dengue system, which uses the trap-level mosquito surveillance data to target areas of high mosquito infestation for control (including source reduction, larvacide, and adulticide)\cite{Eiras2009}.
These control efforts may affect our estimates of the mosquito demographic rates, but should not influence our understanding of dengue dynamics, since we are not interested in the factors driving mosquito dynamics, but rather in how the realized mosquito dynamics (whether forced by human intervention of environmental factors) fit into the broader epidemiological picture.

These local interventions are effective at reducing disease burden in the cities in which they are implemented \cite{Pepin2013}, but long-term epidemiological processes (e.g. fluctuations in human immunity) still seem to be driving disease spread.
Our control simulations account for these processes and offer a suggestion for how an additional city-wide pulse of control might be deployed to supplement existing efforts to reduce mosquito density throughout the city.

That said, we do not anticipate that a single, simultaneous, city-wide pulse of control could be feasibly implemented on top of the existing control efforts.
However, contrary to our assumption of homogeneous mixing between mosquitoes and humans, all mosquitoes may not contribute equally to dengue spread.
In fact, a relatively small proportion of the mosquito population may be responsible for a large proportion of disease spread \cite{Yoon2012}
In particular, structured human movement within the city is likely to induce heterogeneous human-mosquito mixing \cite{Adams2009, Cosner2009a, Stoddard2009}.
In addition, spatial variability in socioeconomic factors within the city may also modulate the extent to which mosquitoes in different parts of the city contribute to disease spread \cite{Mondini2008, Honorio2009, Hu2012, DeMattosAlmeida2007}.
The mechanistic model presented here may be able to suggest when an intervention is likely to be effective, but in order to make the best use of limited resources, spatial prioritization may still be necessary.
This should include not just prioritization of areas with high mosquito abundance, but also areas with disproprtionate risk of disease spread, either due to hetereogeneities in the mixing process or in the distribution of human immunity.

>>>>

In addition, it is important to note that that the data to which we fit our model implicitly reflect the control efforts already enacted by the city.
These control efforts are guided by the MI-Dengue system, which uses the trap-level mosquito surveillance data to target areas of high mosquito infestation for control (including source reduction, larvacide, and adulticide)\cite{Eiras2009}.
These control efforts may affect our estimates of the mosquito demographic rates, but should not influence our understanding of dengue dynamics, since we are not interested in the factors driving mosquito dynamics, but rather in how the realized mosquito dynamics (whether forced by human intervention of environmental factors) fit into the broader epidemiological picture.
That said, our control simulations should be interepreted as exploring the effect of an additional pulse of city-wide control on top of the existing control activities.

We view our simulations of this additional pulse of control primarily as a tool to explore and exploit the long-term feedbacks in the city's epidemiological system, whereas existing control is deployed largely to reduce local (in space and time) disease risk.
This difference in scale highlights the potential for spatial heterogeneities in disease risk within a city.
In particular, structured human movement within the city is likely to induce heterogeneous human-mosquito mixing \cite{Adams2009, Cosner2009a, Stoddard2009}.
In addition, spatial variability in socioeconomic factors within the city may also modulate the extent to which mosquitoes in different parts of the city contribute to disease spread \cite{Mondini2008, Honorio2009, Hu2012, DeMattosAlmeida2007}.
Though our model does not account for these heterogeneities, it is nontheless able to capture the city-wide dynamics reasonably well, suggesting that there may be sufficient mixing to appear homogeneous at the city scale.
Further, though our mechanistic model may be able to suggest when a city-wide intervention is likely to be effective, in order to make the best use of limited resources, spatial prioritization may still be necessary.
Our results emphasize that this should include not just prioritization based on the distribution of mosquito abundance, but also on the distribution of human immunity.
